---
title: "T32"
author: "Nathan Brandt"
date: "3/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load Libraries
```{r, echo=FALSE}
library("tidyverse")
library("googlesheets") #GoogleSheets Info https://cran.r-project.org/web/packages/googlesheets/vignettes/basic-usage.html
library("ggpubr")
```

#Functions
```{r , echo=FALSE}
#Function to convert university date code into decipherable terms, returns the year
convertdate_year <- function(x) {

  if (is.na(x)) {return(x)}
  #first charater is either 0 or 1, 0 = 19, 1 = 20
  #Second two characters are the year, concate to first character transformation
  #Last character is the semester, save to second vector spot
  
  if (substr(x, 1, 1) == 0) {
    date <- paste(19, substr(x, 2, 3), sep = "")
  } else if (substr(x, 1, 1) == 1) {
    date <- paste(20, substr(x, 2, 3), sep = "")
  }
  return(as.numeric(date))
}

#Function to convert university date code into decipherable terms, returns the semester
#May not need
convertdate_semester <- function(x) {  
  if (is.na(x)) {return(x)}
  
  # Last/Fourth character conver to semseter, 2 = Winter, 4 = Spring, 6 = Summer, 8 = Fall
  if (substr(x, 4, 4)) { date <- 'Winter'
  } else if (substr(x, 4, 4)) {date <- 'Spring'
  } else if (substr(x, 4, 4)) {date <- 'Summer'
  } else if (substr(x, 4, 4)) {date <- 'Fall'
  } 
  #return date
  return(as.character(date))
}
```

#To Update Data from PI data sets
```{r}

#Do you want to update from PI Lists
update.pi <- 'No'

if(update.pi == 'Yes') {
  #Reads in list of PIs
  pi.list <- select(gs_read(ss = gs_title("PI_Contact_Info_Tracker")), PI)
  #Adds in first
  update <- gs_read(ss = gs_title(paste("T_32_PhD_Info_",pi.list[1, 1], sep = "")))
  #goes through the rest
  for(x in 2:length(pi.list$PI)) {
    update <- bind_rows(update, gs_read(ss = gs_title(paste("T_32_PhD_Info_",pi.list[x, 1], sep = ""))))
  }


  #creates a new sheet
  gs_new("T32_Update_15_Years_No_PI", ws_title = "Data", input = update, trim = TRUE)

  #Edits old sheet to update
  #gs_edit_cells("T32_Update", ws = "Data", input = t32)
}
```

#Update- For exporting with general filters
```{r}
  update <- student_data # %>% filter(Most_Recent >= 2012) %>% filter(is.na(PI))

  #creates a new sheet
  gs_new("T32_Update", ws_title = "Data", input = update, trim = TRUE)

```
#Aquire Data
```{r}
#read in and check data from Google Sheet
#First Time requires the input of an authroazation key
current.sheet <- 'T_32_Updated_04162018'
student_data <- gs_read(ss = gs_title(current.sheet))

#Convert to Usable Dates - Years only for now
student_data$First_Term <- sapply(student_data$First_Term, convertdate_year)
student_data$Most_Recent <- sapply(student_data$Most_Recent, convertdate_year)
student_data$GABIOLMS <- sapply(student_data$GABIOLMS, convertdate_year)
student_data$GABIOLPHD <- sapply(student_data$GABIOLPHD, convertdate_year)

#Correct data types for proper analysis
student_data$Citz_Stat_Cd <- as.factor(student_data$Citz_Stat_Cd)
student_data$Nyu_Ipeds_Eth_Ld <- as.factor(student_data$Nyu_Ipeds_Eth_Ld)
student_data$Nyu_Ipeds_Eth_Ld <- factor(student_data$Nyu_Ipeds_Eth_Ld, levels = c("Asian/Pacific Islander", "Black", "Hispanic", "Two or More Races", "White", "Not Applicable"))
student_data$Employment_upon_grad_code <- as.factor(student_data$Employment_upon_grad_code)
student_data$Employment_upon_grad_code <- factor(student_data$Employment_upon_grad_code, levels = c("Post-Doctoral Fellowship","Non-Academic Research", "Other"))

#Correct degree typo of BZ to BS
student_data$Deg <- replace(student_data$Deg, student_data$Deg == 'BZ', 'BS')

glimpse(student_data)

#Read in Faculty List for analysis
faculty <- gs_read(ss = gs_title("Faculty_List"))

glimpse(faculty)

#Read in Application Data
app_data <- gs_read(ss = gs_title("BIOL_PHD_2018"))

app_data$Admit_Term <- sapply(app_data$Admit_Term, convertdate_year)
app_data$Admit_Term <- as.factor(app_data$Admit_Term)
app_data$Ipeds_Race_Category <- as.factor(app_data$Ipeds_Race_Category)


glimpse(app_data)

```


#Set global vairable
```{r}
#Filter by Year
filter.year <- 2002
current.year <-2017
```

#Transform Data - For all analysis
```{r}
#For Papers
paper_data <- student_data %>%
  #filter(First_Term >= filter.year) %>%
  #filter(!is.na(GABIOLPHD)) %>%
  select(Student_Name, Paper_1:Paper_16) %>%
  gather(Paper_1:Paper_16, key = 'Papers', value = 'Paper_Citation') %>%
  filter(!is.na(Paper_Citation)) %>%
  mutate(Last_Name = gsub(",.*", "", Student_Name), First_Author = gsub(" .*", "", Paper_Citation) )
 
first_author <-  paper_data %>%
  filter(Last_Name == First_Author) %>%
    select(Student_Name)
first_author <- mutate(arrange(distinct(first_author), Student_Name), First_Author = tabulate(as.factor(first_author$Student_Name)))
  
co_author <-  paper_data %>%
  filter(!(Last_Name == First_Author)) %>%
    select(Student_Name) 
co_author <- mutate(arrange(distinct(co_author), Student_Name), Co_Author = tabulate(as.factor(co_author$Student_Name)))

total_author <-  paper_data %>%
  select(Student_Name) 
total_author <- mutate(arrange(distinct(total_author), Student_Name), Total_Papers = tabulate(as.factor(total_author$Student_Name)))

student_data <- student_data %>% left_join(total_author, by = "Student_Name") %>% left_join(first_author, by = "Student_Name") %>% left_join(co_author, by = "Student_Name")

student_data$Total_Papers <- replace_na(student_data$Total_Papers, 0)
student_data$First_Author <- replace_na(student_data$First_Author, 0)
student_data$Co_Author <- replace_na(student_data$Co_Author, 0)

#For PI commitments
pi_data <- student_data %>%
  filter(First_Term >= filter.year) %>%
  filter(!is.na(PI)) %>%
  select(PI, CO_PI) %>%
  gather(key = 'Position') %>%
  select(value) %>%
  filter(!is.na(value))
names(pi_data) <- c("PI")

copi_data <- student_data %>%
  filter(First_Term >= filter.year) %>%
  filter(!is.na(PI)) %>%
  select(PI, CO_PI) %>% 
  filter(!is.na(CO_PI))

num.comentored <- count(copi_data)
num.pi_comentoring <- length(unique(c(copi_data$CO_PI, copi_data$PI)))

pi_data <- mutate(arrange(distinct(pi_data), PI), Number_Students = tabulate(as.factor(pi_data$PI)))

faculty_list <- faculty %>% select(Last_Name)
names(faculty_list) <- c("PI")

pi_data <-left_join(faculty_list, pi_data, by = "PI")
pi_data$Number_Students <- replace(pi_data$Number_Students, is.na(pi_data$Number_Students), 0)
pi_data$Number_Students <- as.factor(pi_data$Number_Students)


commit_data <- student_data %>%
  filter(First_Term >= filter.year) %>%
  filter(!is.na(PI)) %>%
  select(PI, CO_PI, PhD_commitee_member_1, PhD_commitee_member_2, PhD_commitee_member_3, PhD_commitee_member_4_external) %>%
  gather(key = 'Position') %>%
  filter(!is.na(value)) %>%
  select(value)
names(commit_data) <- c("PI")

commit_data <- mutate(faculty, Number_Committees = str_count(commit_data, faculty$Last_Name))
```

#Graphs
#Adding save to pdf to all graphs, maybe with a if then to control via a global var  on whether or not to produce
#multi.page <- ggarrange(bar, pie, nrow = 1, ncol = 1)
#ggexport(multi.page, filename = "Citzenship.pdf")
#ggsave("StudentsPerYear.pdf")
#Generic Save with Year Cutoff
#ggsave(paste("_",(current.year - filter.year),".jpg", sep = ""))


#Replace Filter of First_Term to Graduation 
```{r}
#How many students per year? (dot and line plot)
student_data %>%
  filter(First_Term >= filter.year) %>%
  ggplot(aes(x = First_Term)) +
  geom_point(stat = 'count') +
  geom_line(aes(group = 1), stat = 'count') +
  ylab("# of Students") +
  xlab("Year") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggsave(paste("NumberStudentPerYear_",(current.year - filter.year),".jpg", sep = ""))

#Demographics (pie or barcharts)
  #Citizenship status
  #Citz Stat Cd	US Citizenship Status (1 = Citizen, 3 = Perm Res, 4 = Non-Resident Alien)
  #Combine Citizin and Non-Residient
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  mutate(Citz_Stat_Cd=replace(Citz_Stat_Cd, Citz_Stat_Cd==3, 1))%>%
  ggplot(aes(x = Citz_Stat_Cd)) +
  geom_bar() +
  ylab("# of Students") +
  xlab("U.S. Citizenship Status") +
  scale_x_discrete(labels = c("Residents", "Non-Residents")) +
  scale_y_continuous(expand=c(0,0), limits = c(0,70)) +
  theme_classic() 

ggsave(paste("StudentCitizenshipStatus_Bar_",(current.year - filter.year),".jpg", sep = ""))

student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  mutate(Citz_Stat_Cd=replace(Citz_Stat_Cd, Citz_Stat_Cd==3, 1))%>%
  ggplot(aes(x = "", fill = Citz_Stat_Cd)) +
  geom_bar(width = 1 ) +
  coord_polar(theta = "y", start=0) +
  theme_void() +
  labs( fill = "U.S. Citizenship Status") +
  scale_fill_discrete(labels = c("Residents", "Non-Residents"))

ggsave(paste("StudentCitizenshipStatus_Pie_",(current.year - filter.year),".jpg", sep = ""))


  #Country of citizenship
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  ggplot(aes(x = Cit)) +
  geom_bar() +
  ylab("# of Students") +
  xlab("Country of Citizenship") +
  scale_y_continuous(expand=c(0,0)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

#ggsave(paste("CountryCitizenship_Bar_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  ggplot(aes(x = "", fill = Cit)) +
  geom_bar(width = 1 ) +
  coord_polar(theta = "y", start=0) +
  theme_void() +
  labs( fill = "Country of Citizenship")

#ggsave(paste("CountryCitizenship_Pie_",(current.year - filter.year),".jpg", sep = ""))


  #Ethnicity
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(Citz_Stat_Cd != 4) %>%
  ggplot(aes(x = Nyu_Ipeds_Eth_Ld)) +
  geom_bar() +
  ylab("# of Students") +
  xlab("Ethnicity of US Residents") +
  scale_y_continuous(expand=c(0,0), limits=c(0,40)) +
  scale_x_discrete(labels = c("Asian/Pacific Islander", "Black", "Hispanic", "White", "Declined to Answer")) +
  theme_classic() 

ggsave(paste("Ethnicity_Bar_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(Citz_Stat_Cd != 4) %>%
  ggplot(aes(x = "", fill = Nyu_Ipeds_Eth_Ld)) +
  geom_bar(width = 1 ) +
  coord_polar(theta = "y", start=0) +
  theme_void() +
  labs( fill = "Ethnicity of US Residents") +
  scale_fill_discrete(labels = c("Asian/Pacific Islander", "Black", "Hispanic", "White", "Declined to Answer"))


ggsave(paste("Ethnicity_Pie_",(current.year - filter.year),".jpg", sep = ""))


  #Qualifications upon entry to program - Unsure what this is? BS vs BA???
# BA = Bachelor of the Arts
# BS = Bachelor of Science
# BBA = Bachelor of Business Administration
# BSA = Bachelor or Science and Arts
# BENG = Bachelor of Engineering
# BZ = Unkonwn - Typo, corrected to BS 
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  ggplot(aes(x = Deg)) +
  geom_bar() +
  ylab("# of Students") +
  xlab("Undergraduate Degree") +
  scale_y_continuous(expand=c(0,0)) +
  theme_classic() 

#ggsave(paste("UndergradDegree_Bar_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  ggplot(aes(x = "", fill = Deg)) +
  geom_bar(width = 1 ) +
  coord_polar(theta = "y", start=0) +
  theme_void() +
  labs( fill = "Undergraduate Degree")

#ggsave(paste("UndergradDegree_Pie_",(current.year - filter.year),".jpg", sep = ""))


#GRE scores - How to look at it? 
#Have 4 columns of data. Verbal and Quantative, both old and new syle of scoring
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  ggplot(aes(x = EV)) +
  geom_bar() +
  ylab("# of Students") +
  xlab("Verbal GRE Scorces (New Scale)") +
  scale_y_continuous(expand=c(0,0)) +
  theme_classic() 

#ggsave(paste("VerbalGRE_New_Bar_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  ggplot(aes(x = EQ)) +
  geom_bar() +
  ylab("# of Students") +
  xlab("Quantative GRE Scorces (New Scale)") +
  scale_y_continuous(expand=c(0,0)) +
  theme_classic() 

#ggsave(paste("QuantGRE_New_Bar_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  ggplot(aes(x = EVP)) +
  geom_bar() +
  ylab("# of Students") +
  xlab("Verbal GRE Scorces Percentage") +
  scale_y_continuous(expand=c(0,0)) +
  theme_classic() 

#ggsave(paste("VerbalGRE_Old_Bar_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  ggplot(aes(x = EQP)) +
  geom_bar() +
  ylab("# of Students") +
  xlab("Quantative GRE Scorces Percentage") +
  scale_y_continuous(expand=c(0,0)) +
  theme_classic() 

#ggsave(paste("QuantGRE_Old_Bar_",(current.year - filter.year),".jpg", sep = ""))


#PhD experience (histograms or boxplot with points overlayed)
  #Time to degree
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  #filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = Years )) +
  geom_histogram(binwidth = 0.5) +
  ylab("# of Students") +
  xlab("Years to PhD") +
  scale_y_continuous(expand=c(0,0)) +
  theme_bw() 

ggsave(paste("StudentYearstoPhD_Histo_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  #filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = "", y= Years )) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', position = position_dodge()) +
  ylab("Years to PhD") +
  xlab("") +
  theme_bw() +
  theme(axis.ticks.x = element_blank())

ggsave(paste("StudentYearstoPhD_Boxplot_",(current.year - filter.year),".jpg", sep = ""))


  #Number of semesters of teaching
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = Semesters_of_teaching )) +
  geom_histogram(binwidth = 1) +
  ylab("# of Students") +
  xlab("Semesters of Teaching") +
  scale_y_continuous(expand=c(0,0)) +
  theme_bw() 

#ggsave(paste("StudentSemestersTeaching_Histo_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = "", y= Semesters_of_teaching )) +
  geom_boxplot() +
  ylab("Semesters of Teaching") +
  theme_bw() 

#ggsave(paste("StudentSemestersTeaching_Boxplot_",(current.year - filter.year),".jpg", sep = ""))


  #Number of published papers - 
#1st author - Condensed
student_data %>%
  mutate(First_Author=replace(First_Author, First_Author>=4, 4))%>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(PI)) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = First_Author )) +
  geom_bar() +
  ylab("# of Students") +
  xlab("# of First Author Papers") +
  scale_x_continuous(breaks = c(0:4), labels = c(0,1,2,3, "4+")) +
  scale_y_continuous(expand=c(0,0), limits = c(0,40)) +
  theme_bw() 

ggsave(paste("Number_1stAuthorPapers_",(current.year - filter.year),".jpg", sep = ""))

#1st author -
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(PI)) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = First_Author )) +
  geom_bar() +
  ylab("# of Students") +
  xlab("# of First Author Papers") +
  scale_x_continuous(breaks = c(0:10)) +
  scale_y_continuous(expand=c(0,0), limits = c(0,40)) +
  theme_bw() 

#ggsave(paste("Number_1stAuthorPapers_Bar_",(current.year - filter.year),".jpg", sep = ""))

#co-author - Condensed
student_data %>%
  mutate(Co_Author=replace(Co_Author, Co_Author>=4, 4))%>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(PI)) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = Co_Author )) +
  geom_bar() +
  ylab("# of Students") +
  xlab("# of Co-Author Papers") +
  scale_x_continuous(breaks = c(0:4), labels = c(0,1,2,3, "4+")) +
  scale_y_continuous(expand=c(0,0), limits = c(0,35)) +
  theme_bw() 

ggsave(paste("Number_CoAuthorPapers_",(current.year - filter.year),".jpg", sep = ""))

#Co author -
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(PI)) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = Co_Author )) +
  geom_bar() +
  ylab("# of Students") +
  xlab("# of Co-Author Papers") +
  scale_x_continuous(breaks = c(0:15)) +
  scale_y_continuous(expand=c(0,0), limits = c(0,40)) +
  theme_bw() 

#ggsave(paste("Number_Co-AuthorPapers_Bar_",(current.year - filter.year),".jpg", sep = ""))


#Total Authored Papers
student_data %>%
  mutate(Total_Papers=replace(Total_Papers, Total_Papers>=4, 4))%>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(PI)) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = Total_Papers )) +
  geom_bar() +
  ylab("# of Students") +
  xlab("# of Papers") +
  scale_x_continuous(breaks = c(0:4), labels = c(0,1,2,3, "4+")) +
  scale_y_continuous(expand=c(0,0), limits = c(0,100)) +
  theme_bw() 

ggsave(paste("Number_TotalPapers_Bar_",(current.year - filter.year),".jpg", sep = ""))


#Subsequent position (pie or barplot)
#Postdoc vs not postdoc
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  filter(!is.na(PI)) %>%
  ggplot(aes(x = (Employment_upon_grad_code))) +
  geom_bar() +
  xlab("Position upon gradutation") +
  ylab("# of Students") +
  scale_x_discrete(labels = c("Post-Doctoral\nFellowship","Non-Academic\nResearch", "Other", "Unkown")) +
  scale_y_continuous(expand=c(0,0), limits = c(0,70)) +
  theme_bw() 

ggsave(paste("PositionUponGrad_Bar_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot(aes(x = "", fill = (Employment_upon_graduation != 'Post-Doctoral Fellowship'))) +
  geom_bar(width = 1 ) +
  coord_polar(theta = "y", start=0) +
  theme_void() +
  labs( fill = "Position upon gradutation") +
  scale_fill_discrete(labels = c("Post-Doctoral Fellowship","Other", "Unkown"))

ggsave(paste("PositionUponGrad_Pie_",(current.year - filter.year),".jpg", sep = ""))


#Postdoc institution
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  filter(Employment_upon_graduation == 'Post-Doctoral Fellowship') %>%
  ggplot(aes(x = Postdoctoral_institution)) +
  geom_bar() +
  ylab("# of Students") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggsave(paste("PostDoc_Institution_Bar_",(current.year - filter.year),".jpg", sep = ""))

  
#Distribution of committee membership (how many committees is each PI on) (histogram) - Student Comittees, need to figure out how to calculate into a graph

#Need to check if we count committee's PI is on due to student
pi_data %>%
  ggplot(aes(x = Number_Students )) +
  geom_bar() +
  annotate("text", x = 5, y = 9, label = paste("Number of Students Co-Mentored =",num.comentored)) +
  annotate("text", x = 5, y = 8, label = paste("Number of PI's Co-Mentoring =",num.pi_comentoring)) +
  ylab("# of PIs") +
  xlab("Students/PI") +
  scale_y_continuous(expand=c(0,0)) +
  scale_x_discrete(breaks = c(0:12), labels = c(0:12)) +
  theme_bw() 

ggsave(paste("StudentsperPI_Bar_",(current.year - filter.year),".jpg", sep = ""))


commit_data %>%
  ggplot(aes(x = Number_Committees )) +
  geom_bar() +
  ylab("# of PIs") +
  xlab("# of Committee Memberships") +
  scale_y_continuous(expand=c(0,0)) +
  theme_bw() 

ggsave(paste("CommitteMembershipsperPI_Bar_",(current.year - filter.year),".jpg", sep = ""))


#Test predictors of PhD experience
    #GRE vs number of papers (scatter plot)
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_point(aes(x = EV, y = First_Author), color = 'red') +
  geom_point(aes(x = EQ, y = First_Author), color = 'blue') +
  theme_bw() 

ggsave(paste("GREvs1stPaper_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() + 
  geom_point(aes(x = (EV+EQ), y = First_Author)) +
  theme_bw() 

student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_point(aes(x = EV, y = Co_Author), color = 'red') +
  geom_point(aes(x = EQ, y = Co_Author), color = 'blue') +
  theme_bw() 

ggsave(paste("GREvsCoPaper_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() + 
  geom_point(aes(x = (EV+EQ), y = Co_Author)) +
  theme_bw() 

student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_point(aes(x = EV, y = Total_Papers), color = 'red') +
  geom_point(aes(x = EQ, y = Total_Papers), color = 'blue') +
  theme_bw() 

ggsave(paste("GREvsTotalPaper_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() + 
  geom_point(aes(x = (EV+EQ), y = Total_Papers)) +
  theme_bw() 


    #citizenship/ethnicity vs number of papers (boxplots)
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
   geom_boxplot(aes(x = Citz_Stat_Cd, y = First_Author)) +
  scale_x_discrete(labels = c("Citizen","Permanent Resisdent", "Non-Resident Alien")) +
  theme_bw()

ggsave(paste("Citizenshivs1stPaper_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
   geom_boxplot(aes(x = Citz_Stat_Cd, y = Co_Author)) +
  scale_x_discrete(labels = c("Citizen","Permanent Resisdent", "Non-Resident Alien")) +
  theme_bw() 

ggsave(paste("CitizenshivsCoPaper_",(current.year - filter.year),".jpg", sep = ""))

student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
   geom_boxplot(aes(x = Citz_Stat_Cd, y = Total_Papers)) +
  scale_x_discrete(labels = c("Citizen","Permanent Resisdent", "Non-Resident Alien")) +
  theme_bw() 

ggsave(paste("CitizenshipvsTotalPaper_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_boxplot(aes(x = Nyu_Ipeds_Eth_Ld, y = First_Author)) +
  theme_bw()

ggsave(paste("Ethiticityvs1stPaper_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
   geom_boxplot(aes(x = Nyu_Ipeds_Eth_Ld, y = Co_Author)) +
  theme_bw() 

ggsave(paste("EthiticityvsCoPaper_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
   geom_boxplot(aes(x = Nyu_Ipeds_Eth_Ld, y = Total_Papers)) +
  theme_bw() 

ggsave(paste("EthiticityvsTotalPaper_",(current.year - filter.year),".jpg", sep = ""))



student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_boxplot(aes(x = Cit, y = First_Author)) +
  theme_bw()

ggsave(paste("Countryvs1stPaper_",(current.year - filter.year),".jpg", sep = ""))



student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
   geom_boxplot(aes(x = Cit, y = Co_Author)) +
  theme_bw() 

ggsave(paste("CountryvsCoPaper_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
   geom_boxplot(aes(x = Cit, y = Total_Papers)) +
  theme_bw() 

ggsave(paste("CountryvsTotalPaper_",(current.year - filter.year),".jpg", sep = ""))


    #Number of papers vs postdoc or not postdoc (boxplots)
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_boxplot(aes(x = (Employment_upon_graduation != 'Post-Doctoral Fellowship'), y = First_Author)) +
  xlab("Position upon gradutation") +
  scale_x_discrete(labels = c("Post-Doctoral Fellowship","Other", "Unkown")) +
  theme_bw()

ggsave(paste("1stAuthorvsPosition_",(current.year - filter.year),".jpg", sep = ""))



student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_boxplot(aes(x = (Employment_upon_graduation != 'Post-Doctoral Fellowship'), y = Co_Author)) +
  xlab("Position upon gradutation") +
  scale_x_discrete(labels = c("Post-Doctoral Fellowship","Other", "Unkown")) +
  theme_bw()

ggsave(paste("CoAuthorvsPosition_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_boxplot(aes(x = (Employment_upon_graduation != 'Post-Doctoral Fellowship'), y = Total_Papers)) +
  xlab("Position upon gradutation") +
  scale_x_discrete(labels = c("Post-Doctoral Fellowship","Other", "Unkown")) +
  theme_bw()
  
ggsave(paste("TotalAuthorvsPosition_",(current.year - filter.year),".jpg", sep = ""))


    #Semesters teaching vs number of papers (scatter)
student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_point(aes(x = Semesters_of_teaching, y = First_Author)) +
  xlab("Semesters of Teaching") +
  theme_bw()

ggsave(paste("Teachingvs1stAuthor_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_point(aes(x = Semesters_of_teaching, y = Co_Author)) +
  xlab("Semesters of Teaching") +
  theme_bw()

ggsave(paste("TeachingvsCoAuthor_",(current.year - filter.year),".jpg", sep = ""))


student_data %>%
  filter(GABIOLPHD >= filter.year) %>%
  filter(!is.na(GABIOLPHD)) %>%
  ggplot() +
  geom_point(aes(x = Semesters_of_teaching, y = Total_Papers)) +
  xlab("Semesters of Teaching") +
  theme_bw()
ggsave(paste("TeachingvsTotalAuthor_",(current.year - filter.year),".jpg", sep = ""))


```

```{r}
#Grad School Application, Admits, and Enrollments
app_years = c("Fall, 2013", "Fall, 2014", "Fall, 2015", "Fall, 2016", "Fall, 2017", "Fall, 2018")

app_data %>%
  filter(Ipeds_Race_Category != 9) %>% #Filter to remove non-citizens and non-permenant residents, Using International status as a proxity, holds up when compared to T32 data on enrolled students
  ggplot(aes(x = Admit_Term)) +
    geom_bar(data = . %>% filter(App == 1), aes(fill = "App"), width = 0.8, colour = 'black') +
    geom_text(data = . %>% filter(App == 1), stat='count', aes(label=..count..), vjust = -0.5, size = 2) +
    geom_bar(data = . %>% filter(Admit == 1), aes(fill = "Admit"), width = 0.4, colour = 'black') +
    geom_text(data = . %>% filter(Admit == 1), stat='count', aes(label=..count..), vjust = -0.5, size = 2) +
    #geom_bar(data = . %>% filter(Accept == 1), aes(fill = "Accept")) +
    #geom_text(data = . %>% filter(Accept == 1), stat='count', aes(label=..count..), vjust = -1, size = 1) +
    geom_bar(data = . %>% filter(Enroll == 1), aes(fill = "Enroll"), width = 0.2, colour = 'black')  +
    geom_text(data = . %>% filter(Enroll == 1), stat='count', aes(label=..count..), vjust = -0.5, size = 2) +
    #ggtitle("Graduate School Applicants, Admits, & New Enrollments") +
    ggtitle("Graduate School Applicants, Admits, & New Enrollments", subtitle = "Eligible Applicants") +
    scale_y_continuous(expand=c(0,0), limits = c(0,280)) +
    scale_x_discrete(labels = app_years) +
    scale_fill_manual(breaks = c("App","Admit", "Enroll"),  values=c("grey", "wheat", "red"), labels = c("Applicants", "Admitted Applicants", "New Enrollments")) +
    theme(plot.subtitle = element_text(hjust = 0.4), axis.title = element_blank(), axis.text.y = element_blank(), axis.text.x = element_text(size = 10 ), axis.ticks = element_blank(), panel.background = element_blank(), axis.line.x = element_line(), legend.title = element_blank(), legend.position = "left")


#ggsave("Grad_Apps_All.jpg")
ggsave("Grad_Apps_Eligible.jpg")

app_eth_code = c("White","Black","Hispanic","Asian/Pacific\nIslander","American\nIndian/Alaskan\nNative","Declined\nto Answer","Native Hawaiian\nOther Pac Island","Two or more\nraces") 
app_data %>%
  filter(Ipeds_Race_Category != 9) %>% #Filter to remove non-citizens and non-permenant residents, Using International status as a proxity, holds up when compared to T32 data on enrolled students
  ggplot(aes(x = Ipeds_Race_Category)) +
    geom_bar(data = . %>% filter(App == 1), aes(fill = "App"), width = 0.8, colour = 'black') +
    geom_text(data = . %>% filter(App == 1), stat='count', aes(label=..count..), vjust = -0.5, size = 2) +
    geom_bar(data = . %>% filter(Admit == 1), aes(fill = "Admit"), width = 0.4, colour = 'black') +
    geom_text(data = . %>% filter(Admit == 1), stat='count', aes(label=..count..), vjust = -0.5, size = 2) +
    geom_bar(data = . %>% filter(Enroll == 1), aes(fill = "Enroll"), width = 0.2, colour = 'black')  +
    geom_text(data = . %>% filter(Enroll == 1), stat='count', aes(label=..count..), vjust = -0.5, size = 2) +
    scale_x_discrete("Ethnicity", labels = app_eth_code) +
    scale_y_continuous(expand=c(0,0), limits = c(0,450)) + 
    scale_fill_manual(breaks = c("App","Admit", "Enroll"),  values=c("grey", "wheat", "red"), labels = c("Applicants", "Admitted Applicants", "New Enrollments")) +
    theme(axis.title = element_blank(),  axis.text.y = element_blank(), axis.text.x = element_text(size = 10, angle = 90, vjust = 0.5), axis.ticks = element_blank(), panel.background = element_blank(), axis.line.x = element_line(), legend.title = element_blank(), legend.position = "left") 

ggsave("Grad_Apps_Eligible_Ethnicity.jpg")


```

#Tables
``` {r}
success <- tibble( 
  Success = c("First Author Publications Per Student", "Total Publications Per Student", "Dean's Dissertation Award", "Kopaz Teaching Award", "F31 Pre-Doctoral Fellowships", "NSF Pre-Doctoral Fellowships", "Other Pre-Doctoral Fellowships"), 
  During_Last_15_Years = c(0), 
  During_Last_5_Years = c(0))

academic_career <- tibble( 
  Academic_Careers = c("Post-Doctoral Positions", "Faculty Positions", "Teaching Positions"), 
  Last_15_Years = c(0), 
  Last_5_Years = c(0))

other_career <- tibble( 
  Non_Academic_Careers = c("Editing", "Industry", "Management", "Other"), 
  Last_15_Years = c(0), 
  Last_5_Years = c(0))
```

#Table_Data
```{r}
View(student_data %>% filter(Most_Recent == 2017) %>% select(Student_Name,PI))

#current Students
View(summarize(student_data %>% filter(Most_Recent == 2017) %>% select(Student_Name), n()))

#Number of Student per particpating faculty
sum(str_count(student_data %>% filter(Most_Recent == 2017) %>% select(Student_Name, PI), faculty$Last_Name))

participating_faculty_data <- student_data %>%
  filter(Most_Recent == 2017) %>% 
  select(Student_Name,PI) %>% 
  filter(!is.na(PI)) %>%
  select(PI)

participating_faculty_data <- mutate(faculty, Number_Student = str_count(participating_faculty_data , faculty$Last_Name)) 

View(participating_faculty_data %>% filter(Participating == 'Yes'))


```